The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt

p. 3, Fig. 2, caption or text: You should briefly comment on why the quasar
distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
sensitivity across the filter curves, and/or the onset of complete GP-troughs at
z>5.7?

	[And I think this is where some of the missing objects come in??
	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.]

p. 4, Fig. 3: Can you plot the small dots somewhat bigger for better visibility
without loss of information?

	We have updated the plot to make the dots bigger and the revised catalogue.

@@

		We have added approriated words in the text to address this good point.

p. 6 Table 3: Should mention that the number of significant digits listed here
for the YJHK W1--W4 mags is not always warranted, but needed to verify the small
VIRCAM-WFCAM offsets in Table 5, This table is a very useful check of your global
photometric zeropoints.

p. 7, very end of 3.1.1: Quote the (effective) VSA and SDSS quasar IR observing
epochs here, in case these clearly discrepant magnitudes are due to variability.

SDSS J0349+0034 was observed on MJD=54062.4 by WFCAM and MJD=55540.6 (average of 
3 epochs from 55537 to 55542) by VISTA. We have updated the text with these values.

### 2020-01-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Modified Fig 3, coverage maps with new QSOs and bigger symbols
Modified Sec 3.11 with epoch numbers

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
  % {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
 {figures/CoverageMaps_VHzQ_forpaper.pdf}
  \centering
  \caption[]
  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING
(DR5; blue) and ULAS (DR11; red), the most recent public releases of
the 4 main surveys. The VH$z$Qs are given by black dots.}
  \label{fig:coverage}
\end{figure}

@@

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 19.13$\pm$0.24, while for the
  VSA $K_s$-band this is 18.36$\pm$0.10 mag.

>>>>

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=0mm 0mm 0mm 10mm]
  % {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
 {figures/CoverageMaps_VHzQ_forpaper.pdf}
  \centering
  \caption[]
  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING
(DR5; blue) and ULAS (DR11; red), the most recent public releases of
the 4 main surveys. The VH$z$Qs are given by black dots.}
  \label{fig:coverage}
\end{figure}

@@

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 19.13$\pm$0.24 (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 18.36$\pm$0.10 mag
  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
  observations are $\sim4$ years apart.
